Significant declines in standardised test scores due to COVID-19 school closures disproportionately affect vulnerable students: A replication analysis using data from the United States and a case study on the Netherlands

### 2024-02-14 paper/paper.qmd
Improved Figure 2
Combined the 4 seperate race figures into 1 panel of data

```{r setup}
#| echo: false
#| message: false
#| warning: false
library(here) 
library(tidyverse)
library(knitr)
library(janitor)
library(kableExtra)
library(DiagrammeR)
library(readxl)
library(patchwork)

@@

```{r}
#| label: fig-white
#| echo: false
#| fig-cap: "Share White"
ggplot(averaged_white_share, aes(x = QUANTILE_LABEL, y = average)) +
  geom_bar(stat = "identity", fill = "skyblue", width = 0.5) +
  labs(x = "Quantile Label", y = "Average") +
  ggtitle("Average Days Virtual by Quantile") +
  geom_text(aes(label = sprintf("%.0f", average)), 
            position = position_dodge(width = 0.9), 
            vjust = -0.5, size = 3) +
  labs(x = "Quantile", y = "Average Days Virtual") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
#| label: fig-black
#| echo: false
#| fig-cap: "Share Black"
ggplot(averaged_black_share, aes(x = QUANTILE_LABEL, y = average)) +
  geom_bar(stat = "identity", fill = "skyblue", width = 0.5) +
  labs(x = "Quantile Label", y = "Average") +
  ggtitle("Average Days Virtual by Quantile") +
  geom_text(aes(label = sprintf("%.0f", average)), 
            position = position_dodge(width = 0.9), 
            vjust = -0.5, size = 3) +
  labs(x = "Quantile", y = "Average Days Virtual") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
#| label: fig-asian
#| echo: false
#| fig-cap: "Share Asian"
ggplot(averaged_asian_share, aes(x = QUANTILE_LABEL, y = average)) +
  geom_bar(stat = "identity", fill = "skyblue", width = 0.5) +
  labs(x = "Quantile Label", y = "Average") +
  ggtitle("Average Days Virtual by Quantile") +
  geom_text(aes(label = sprintf("%.0f", average)), 
            position = position_dodge(width = 0.9), 
            vjust = -0.5, size = 3) +
  labs(x = "Quantile", y = "Average Days Virtual") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
#| label: fig-hispanic
#| echo: false
#| fig-cap: "Share Hispanic"
ggplot(averaged_hispanic_share, aes(x = QUANTILE_LABEL, y = average)) +
  geom_bar(stat = "identity", fill = "skyblue", width = 0.5) +
  labs(x = "Quantile Label", y = "Average") +
  ggtitle("Average Days Virtual by Quantile") +
  geom_text(aes(label = sprintf("%.0f", average)), 
            position = position_dodge(width = 0.9), 
            vjust = -0.5, size = 3) +
  labs(x = "Quantile", y = "Average Days Virtual") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))
```

>>>>

```{r setup}
#| echo: false
#| message: false
#| warning: false
library(here) 
library(tidyverse)
library(knitr)
library(janitor)
library(kableExtra)
library(DiagrammeR)
library(readxl)
library(patchwork)
library(gridExtra)

@@

```{r}
#| label: fig-white
#| echo: false
#| fig-cap: "Average Virtual School Days by Share of Race"

whiteplot <- ggplot(averaged_white_share, aes(x = QUANTILE_LABEL, y = average)) +
  geom_bar(stat = "identity", fill = "skyblue", width = 0.5) +
  labs(x = "Quantile", y = "Average Days Virtual") +
  ggtitle("White Share") +
  geom_text(aes(label = sprintf("%.0f", average)), 
            position = position_dodge(width = 0.9), 
            vjust = -0.5, size = 3) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, size = 10),
                axis.title.x = element_text(size = 9),
                axis.title.y = element_text(size = 9),
        axis.text.y = element_text(size = 7.5)) +
  ylim(0, 60)

blackplot <- ggplot(averaged_black_share, aes(x = QUANTILE_LABEL, y = average)) +
  geom_bar(stat = "identity", fill = "skyblue", width = 0.5) +
  labs(x = "Quantile", y = "Average Days Virtual") +
  ggtitle("Black Share") +
  geom_text(aes(label = sprintf("%.0f", average)), 
            position = position_dodge(width = 0.9), 
            vjust = -0.5, size = 3) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, size = 10),
                axis.title.x = element_text(size = 9),
                axis.title.y = element_text(size = 9),
        axis.text.y = element_text(size = 7.5)) +
  ylim(0, 60)

asianplot <- ggplot(averaged_asian_share, aes(x = QUANTILE_LABEL, y = average)) +
  geom_bar(stat = "identity", fill = "skyblue", width = 0.5) +
  labs(x = "Quantile", y = "Average Days Virtual") +
  ggtitle("Asian Share") +
  geom_text(aes(label = sprintf("%.0f", average)), 
            position = position_dodge(width = 0.9), 
            vjust = -0.5, size = 3) +
  labs(x = "Quantile", y = "Average Days Virtual") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, size = 10),
                axis.title.x = element_text(size = 9),
                axis.title.y = element_text(size = 9),
        axis.text.y = element_text(size = 7.5)) +
  ylim(0, 60)

hispanicplot <- ggplot(averaged_hispanic_share, aes(x = QUANTILE_LABEL, y = average)) +
  geom_bar(stat = "identity", fill = "skyblue", width = 0.5) +
  labs(x = "Quantile", y = "Average Days Virtual") +
    ggtitle("Hispanic Share") +
  geom_text(aes(label = sprintf("%.0f", average)), 
            position = position_dodge(width = 0.9), 
            vjust = -0.5, size = 3) +
  labs(x = "Quantile", y = "Average Days Virtual") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, size = 10),
                axis.title.x = element_text(size = 9),
                axis.title.y = element_text(size = 9),
        axis.text.y = element_text(size = 7.5)) +
  ylim(0, 60)

grid.arrange(
  whiteplot, blackplot, asianplot, hispanicplot,
  nrow = 2, 
  heights = c(1, 1)
)

```
